Analysis of bulk void regions

### 2014-05-29 cosmic_voids.tex
Updating paper

  \includegraphics[trim = 25mm 200mm 18mm 15mm, clip, keepaspectratio=true,
  width=0.5\textheight]{./figures/cosmicweb_FA_Tweb.pdf}

  \includegraphics[trim = 25mm 200mm 18mm 15mm, clip, keepaspectratio=true,
  width=0.5\textheight]{./figures/cosmicweb_FA_Vweb.pdf}

>>>>

  \includegraphics[trim = 16mm 10mm 5mm 8mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 10mm 5mm 8mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
